\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{epsfig}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{amsmath,amssymb,amsthm}



% FILL IN THE SPECIFICS OF EACH HOMEWORK HERE
\newcommand{\course}{CS 364}
\newcommand{\semester}{Spring 2013}
\newcommand{\name}{Artificial Intelligence}
%%%
%%%
%%% PLEASE FILL OUT YOUR NAME AND THE HWK NUMBER
%%%
%%%
\newcommand{\hwk}{Homework 1 Solutions}
\newcommand{\student}{Charles Marks, Isaac Hollander McCreery, Nick Tobin-Jones}

\newtheorem{lemma}{Lemma}
\newtheorem*{lem}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{notation}{Notation}
\newtheorem*{claim}{Claim}
\newtheorem*{fclaim}{False Claim}
\newtheorem{observation}{Observation}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem*{rt}{Running Time}




%%% You can ignore the following stuff, it's just for formatting purposes
\textheight=8.6in
\setlength{\textwidth}{6.44in}
\addtolength{\headheight}{\baselineskip} 
% enumerate uses a), b), c), ...
\renewcommand{\labelenumi}{\alph{enumi})}
% Sets the style for fancy pages (namely, all but first page)
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.4pt}
% Changes style of plain pages (namely, the first page)
\fancypagestyle{plain}{
  \fancyhf{}
  \renewcommand\headrulewidth{0pt}
  \renewcommand\footrulewidth{0.4pt}
  \renewcommand{\headrule}{}
  }
% Changes the title box on the first page
\renewcommand\maketitle{
\begin{center}
\begin{tabular*}{6.44in}{l @{\extracolsep{\fill}}c r}
\bfseries  &  & \bfseries \course ~\semester \\
\bfseries&  & \bfseries  \hwk  \\
\bfseries   &   &  \bfseries \student \\ 
\end{tabular*}
\end{center} }




%%
%%
%% THE REAL STUFF STARTS HERE
%%
%%
\begin{document}
\maketitle
\thispagestyle{plain}

%%% PLEASE PLACE THE HONOR CODE AND YOUR NAME/SIGNATURE HERE
\noindent Honor Code: 


\section*{Question 1}

\textbf{a.}  Get the red bull.
\begin{itemize}
\item \textbf{State Space:}  We have 4 locations a,b,c,d  and let $L = \{a,b,c,d\}$ and our states are triples of $L \times L \times L$
\item \textbf{Start State:}
\item \textbf{Available Actions:}
\item \textbf{Successor Function:}
\item \textbf{Goal Test:}
\item \textbf{Cost Function:}

\end{itemize}

\textbf{b.}  Name some actors.
\begin{itemize}
\item \textbf{State Space:} Ordered sets of actors.  (no repeats)
\item \textbf{Start State:}
\item \textbf{Available Actions:} Add another actor to the set
\item \textbf{Successor Function:}
\item \textbf{Goal Test:} If the last actor has no costars that haven't been named.
\item \textbf{Cost Function:}

\end{itemize}

\textbf{c.} 4 gallons of water
\begin{itemize}
\item \textbf{State Space:} Ordered pairs $\{0,1,2,3,4,5\} \times \{0,1,2,3\}$.  
\item \textbf{Start State:}
\item \textbf{Available Actions:} Fill empty and transfer
\item \textbf{Successor Function:}
\item \textbf{Goal Test:} 
\item \textbf{Cost Function:}

\end{itemize}

\textbf{d.} Get that shit across
\begin{itemize}
\item \textbf{State Space:} Ordered quadruples of $\{0,1\}$ crossed 4 times where 0 represents one side and 1 represents another side. 
\item \textbf{Start State:}
\item \textbf{Available Actions:} Fill empty and transfer
\item \textbf{Successor Function:}
\item \textbf{Goal Test:} 
\item \textbf{Cost Function:}

\end{itemize}

\section*{Question 2}

\emph{Theorem.}
If a heuristic is consistent, then it must be admissible.

\begin{proof}
Suppose that the heuristic $h: Q \rightarrow \mathbb{R}^+$, where $Q$ is the state space for a given
problem, is consistent.  Then for any $n \in Q$, $h(n) \leq c(n, a, n') + h(n')$ for all successors
$n'$ of $n$, where $c(n, a, n')$ is the cost of moving from $n$ to $n'$.  But, similarly, $h(n') \leq
c(n', a, n'') + h(n'')$ for all successors $n''$ of $n'$.  We may continue in this fashion until we
get to some successor $n^k$ that is a goal state, and whose heuristic is zero:
\[
h(n) \leq c(n, a, n') + h(n') \leq c(n, a, n') + c(n', a, n'') + h(n'') \leq \dots \leq
\sum_{i = 1}^k c(n^{i-1}, a, n^i),
\]
but one of such sums is the minimum cost path from $n$ to a goal state $n^k$, so
\[
h(n) \leq \sum_{i = 1}^k c(n^{i-1}, a, n^i) = h^*(n),
\]
and thus $h$ is admissible.
\end{proof}

\emph{Theorem.}
If a heuristic is admissible, then it is not necessarily consistent.

\begin{proof}
Consider the following example:

\vspace*{1in}

where $h(n) = 3$ and $h(n') = 1$.  Then $h(n) = 3 = h^*(n)$ and $h(n') = 1 \leq 2 = h^*(n')$,
so $h$ is admissible.  However, $h(n) = 3 \nleq 2 = c(n, a, n') + h(n')$, so $h$ is not consistent.
\end{proof}

\end{document}
